Mapping factors associated with adolescents' emotion dysregulation: A text-mining based systematic review

### 2020-11-28 manuscript.Rmd
Add baseline

abstract: |
  Adolesence is a developmentally sensititve period for emotion dysregulation. Although substantial empirical research has addressed relevant risk factors, an integrating framework is lacking. This systematic review of 6305 papers uses text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation. One analysis focused on author-provided keywords; a second analysis parsed the abstracts. Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators”. We reported term/document frequency, and force-directed graphs of term co-occurrence. These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms. This research constitutes a first step towards integrating the literature, and may inspire future empirical and theoretical work.
It also illustrates how text mining reviews may complement narrative reviews. <!--SH I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->

@@

<!-- Emotion regulation in adolescence is important -->
A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five people, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
The present review set out to address this question.
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, as the topic has been investigated from different (sub)disciplines.
This systematic review seeks to overcome this limitation by adopting a novel method -
text mining based bibliographic analysis - to map all factors currently
considered to be relevant to adolescent emotion regulation.
Text mining can reveal important topics in a body of literature,
and reveal which constructs are often studied together.
It is therefore uniquely suited to comprehensively review a prolific but fragmented field,
potentially revealing topics and connections missed by narrative reviewers,
and laying the groundwork for future empirical and theoretical work.
<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case? Is there some primary thesis/argument that will be advanced? It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
<!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->

@@

The structure of the empirical literature on adolescents' emotion regulation is best understood against the backdrop of the existing theoretical landscape.
This allows us to see in what respects 
phenomenon.
We therefore provide a summary review of the theoretical landscape as context for our
empirical contribution.
Several recent publications provide more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
It is apparent from these reviews that, although many theories are *relevant* for emotion regulation development in adolescence, few have addressed this topic directly.
Fewer theories still have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019].
There is thus a need for more integrative theory formation [see @riedigerEmotionRegulationAdolescence2014].

Hall's notion of "storm and stress" is one of the oldest relevant theories of adolescents' emotional development [see
@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
self-control and increase reactivity, leading to difficulties in emotion
regulation, conflict with parents, and risky behavior.
In modern theories, this notion of diminished self-control and increased emotional reactivity has been - although it is now considered to be a normative change that facilitates emotional maturation
[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].

@@

Two theories widely invoked to frame research on development, including
emotional development, are Bronfenbrenner's bioecological model, and Sameroff's
transactional model. Bronfenbrenner's model
[@bronfenbrennerBioecologicalModelHuman2007] describes how the environment
shapes individual development. Each individual is imbued with certain
biological predispositions, and develops over time, in interaction with
contextual influences. These influences range from the microsystem, composed of
those people close to the individual, to the macrosystem, consisting of
indirect political and economic influences, to the exosystem, consisting of
cultural norms and values. Sameroff's model is somewhat compatible with the
bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
on the interplay between nature and nurture. It conceptualizes development as a
product of reciprocal influences between the child and the environment.
Sameroff distinguishes between proximal influences, for instance, through
parents (the microsystem in Bronfenbrenner's model), and distal influences;
structural factors indirectly shaping development, like socio-economic status,
schools, and the community (macro- and exosystem). With increasing age, distal
influences gradually gain ground on proximal influences.
<!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->

@@

This emphasis on social influences and neurocognitive development is reflected in many theories.
Some of these focus primarily on neurocognitive development.
For example, polyvagal theory closely links emotional experience
- and regulation - to autonomous nervous system functioning
[@porgesOrientingDefensiveWorld1995].
A more recent neurocognitive theory, with
substantial relevance to adolescents' emotion regulation development, is Crone
and Dahl's model of social-affective engagement and goal flexibility
[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
Crone and Dahl argue that the developmental
asymmetry between motivational and inhibitory brain circuits gives rise to a
"maturity gap" in middle adolescence. 
What sets Crone and Dahl apart from related writings, however, 
is the greater attention to adolescents' diverging destinies:
the question why some youngsters flourish while others languish.
They argue that adolescents' cognitive engagement is dynamically responsive to
social and motivational goal salience. This flexibility, on the one hand,
prepares adolescents to effectively engage cognitive systems in novel
challenging situations in a way that facilitates developing mature regulatory
abilities. On the other hand, it places them at risk to act impulsively in
pursuit of peer approval. In terms of explanans,
this theory focuses primarily on cognitive factors
and the role of peers, with less attention to factors such as parenting.

Other theories emphasize socialization to a greater extent.
One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
It describes three pathways through which parents shape emotion regulation
development: Through observation and modeling, parenting practices, and the
emotional family climate, which in turn involves attachment and marital
relationship quality. Morris and colleagues also emphasize the relevance of
fathers and siblings, and others have adapted the tripartite model to describe
the role of peers in adolescents' emotion regulation development
[@reindlSocializationEmotionRegulation2016].
A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
internalization model of emotional development. 
Unique aspects emphasized in this theory are the interplay between emotion and communication,
and the internalization of the cultural symbolic function of emotion.
<!--Like Sroufe, Holodynski describes an age graded transition from
interpersonal to intrapersonal emotion regulation.
In doing so, Holodynski applies Vygotsky's theory of development to the domain of
emotion, and presents a detailed integrated model of emotional experience and
regulation.-->

Finally, theories of the phenomenon of emotion regulation offer a unique perspective on potential proximal drivers of emotion regulation development.
One influential theory is Gross'
[-@grossHandbookEmotionRegulation2013] process model, which describes the
process of emotion regulation, from eliciting cue to ultimate response.
According to Gross, individuals use strategies to modulate the different stages of this process,
consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
information processing theory of emotion also describe the role of cognitive
processes and strategies in emotion experience and regulation
[@lemeriseIntegratedModelEmotion2000].

<!--Theories like this are particularly relevant to a fine-grained
understanding of the process of emotion regulation, but their developmental
relevance has unfortunately not yet been considered (REF Buss). -->

<!--Parents are widely considered to be the primary proximal influence driving
emotion regulation development.

Yet several limitations remain.
@coe-odessEmergentEmotionsAdolescence2019;
instead takes an inductive approach to map the correlates of adolescents'
emotion regulation based on all available literature.

@@

## Shortcomings of existing theory

Despite the abundance of relevant theory,
the existing literature has several limitations when the goals is to
identify which
risk factors render some adolescents more susceptible
to maladaptive emotional development than others.
One crucial shortcoming
is the lack of explicit attention to the life stage of adolescence. This is
unfortunate, as empirical research consistently indicates that adolescence is a
crucial life stage for emotion regulation development. Adolescence differs
qualitatively from infancy, childhood, and adulthood. It is therefore
questionable whether theories focused on different ages can be generalized to adolescents.
By contrast, some theories focus on adolescence specifically [e.g.,
@croneUnderstandingAdolescencePeriod2012], but only address emotion regulation
in passing.
A second, related, shortcoming is that some relevant theories lack
a developmental component <!--, and thus lack a well-substantiated
understanding of developmental processes--> [see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. 
A third shortcoming is that theories
vary widely in scope: Some are very broad and all-encompassing, but somewhat
non-specific, such as the biopsychosocial models of Bronfenbrenner and
Sameroff. Others describe a specific phenomenon in great detail, but are not
embedded in a larger unifying framework. Examples include Morris' tripartite
model, Crone and Dahl's model, and polyvagal theory. It would be beneficial to
bridge these levels of analysis.
One limitation echoed across many
publications in this field is that more theory formation is required to provide
a unified framework that could guide future empirical work.
The present study
seeks to lay the groundwork for such theory development,
by providing an inductive conceptual
review of the field.

@@

Whereas theory provides a top-down understanding of an area of research,
literature reviews can provide a bottom-up, inductive understanding. Given the
noted absence of a single overarching theory, reviews might provide additional
insight into factors considered relevant in the etiology of adolescents'
emotion regulation competencies. For example, a review by
@bariolaChildAdolescentEmotion2011 addresses individual psychological factors
such as temperament, and biological factors like neurocognitive development and
genetic predispositions. Furthermore, the authors address proximal social influences,
including parents, teachers, and peers, and specific mechanisms through which
these individuals exert their influence, including parenting and modeling.
Finally, they address distal factors, including the role of culture and the
media. Barriola and colleagues also offer recommendations for future research,
<!--most notably, they call for a robust theoretical framework to guide future
research.--> calling for research on the role of parents beyond early
childhood, and including the role of fathers - a limitation which has since
been addressed by a new wave of empirical research on fathers' role in
emotional development [@vanlissaRoleFathersMothers2019;
@vanlissaMothersFathersQuantitative2020].

Another review, by @coe-odessEmergentEmotionsAdolescence2019, offers a nuanced
discussion of several issues that complement prior publications in this field.
For instance, the authors cover the implications of physiological changes in
detail, including neurocognitive development and pubertal maturation. As
adolescents become increasingly individuated, conflict with parents peaks. This
conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood
variability and dispositional emotion dysregulation [see also
@vanlissaCostEmpathyParentadolescent2017]. As parental importance diminishes,
adolescents become increasingly oriented towards peers. This includes increased
sensitivity to social status and norms, along with the associated increase in
peer pressure and risk taking. Pubertal development also initiates the
emergence of sexual and romantic behavior, and the intensification of both
biological sex differences and gender stereotyped behavior. With regard to the
process of emotion regulation, Coe-Odess and colleagues discuss the importance
of strategies, and point out that, in addition to negative emotionality,
positive emotionality also peaks in adolescence. Relatedly, the authors
describe how hormonal changes precipitate an increased stress response, which
might help explain adolescents' greater susceptibility to emotion
dysregulation. Finally, going beyond the implications of cognitive development
discussed in other publications, the authors discuss how an greater capacity
for abstract thought relates to identity formation - a key challenge in
adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
understanding, and by extension, empathy [see also
@vanlissaLongitudinalInterplayAffective2014].

There are notable parallels between the relevant factors highlighted by these
narrative reviews, and the aforementioned theoretical literature. Nevertheless,
these literature reviews also touch upon issues that have received little
attention in theoretical work. This highlights the value of both top-down and
bottom-up approaches to understanding the phenomenon of adolescents' emotion
regulation. One remaining limitation is that, to date, all reviews in this
field have been unstructured narrative reviews. The present publication seeks
to complement preceding work by conducting a comprehensive empirical
literature review, and mapping the factors associated with adolescent emotion
regulation.

@@

@@

The present paper aims to develop a nomological network of the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. A nomological network is a diagrammatic representation of a
phenomenon; a proto-theoretical device that describes relationships between
constructs relevant to the theory [see @alaviAligningTheoryMethodology2018]. It is a precursor to a more
explicit theory of the phenomenon. The present paper uses an inductive approach
to develop this nomological network. First, we conduct a systematic search to
elicit a corpus of relevant literature. Second, we use text mining techniques
to extract relevant constructs from the corpus. Third, we use a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we map interrelations between these constructs. Fifth, we classify
contstructs as potential predictors or outcomes.
<!--, and we categorize predictors
by level of analysis-->
<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

All searches were conducted on Web of Science. The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
manually constructed a reference set of 15 articles. Then we constructed a
search string to retrieve these articles from Web of Science. The search was
overly inclusive, returning 29 records. As these were all highly relevant, we
updated the reference set to include all 29 results. Next, we tested our search
string, which consisted of synonyms of emotion regulation and adolescence: <!--
### Reference set Our reference set is documented in `reference_set.bib`. -->
```
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
```
This string returned 6653 results, and matched 25 of the 29 records in the
reference set. Three search terms could be added to match all 29 reference set
items. The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms
of emotion regulation, added 191 new hits. However, many of these hits were not
directly relevant to emotion regulation. The term `"development*"`, as synonym
of adolescence, added 3628 new hits, many of which were not focused on the age
range of adolescence. We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
For this analysis, we used the term frequency/inverse document frequency (TF-IDF) to select terms
used frequently in a document, but not used frequently in the corpus,
which could therefore be more diagnostic of subgroup membership.
Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.
We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
Thus, no interpretable subcorpora could be identified,
and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->

@@

# General discussion

>>>>

abstract: |
  <!--RK: Wat is je onderzoeksvraag?-->Adolesence is a developmentally sensititve period for emotion dysregulation.
  Although substantial empirical research has addressed relevant risk factors, an integrating framework is lacking. This systematic review of 6305 papers uses text mining to map correlates of adolescents’ (ages 10-25) emotion dysregulation. One analysis focused on author-provided keywords; a second analysis parsed the abstracts. Terms were coded as putative “Causes”, “Outcomes”, “Protective factors”, or “Indicators”. We reported term/document frequency, and force-directed graphs of term co-occurrence. These results reﬂected constructs commonly featured in theory and narrative reviews, but also identified underrepresented terms. This research constitutes a first step towards integrating the literature, and illustrates how text mining reviews may complement narrative reviews. <!--may inspire future empirical and theoretical work. SH: I would end with a more memorable take-home about how text-mining can be useful to researchers (e.g., when topics are of multi-disciplinary interest but each field has their own preferred methods and/or terminology)-->

@@

<!-- Emotion regulation in adolescence is important -->
A key developmental challenge in adolescence is acquiring mature emotion
regulation skills [@croneUnderstandingAdolescencePeriod2012;
@zimmermannEmotionRegulationEarly2014]. Emotion regulation is integral to
mental health [@aldaoEmotionregulationStrategiesPsychopathology2010;
@schaferEmotionRegulationStrategies2017; @braetEmotionRegulationChildren2014]
and social functioning [@reindlSocializationEmotionRegulation2016]. For as many
as one in five, adolescence marks the onset of emotion
regulation-related mental illness, which can persist throughout the life course
[see @leeAdolescentMentalHealth2014]. 
It is therefore crucial to identify which
risk factors and environmental hazards render some adolescents more susceptible
to emotional difficulties than others. <!--SH: Main goal of paper -->
The present review set out to address this question.
Although there is an abundance of empirical work on adolescents' emotion regulation, the literature is somewhat fragmented, because the topic has been investigated from different (sub)disciplines.
As a result, there is a lack of unifying theory, and narrative reviews fall short of comprehensive coverage of the vast but diffuse literature [@bussTheoriesEmotionalDevelopment2019].

The present systematic review seeks to overcome this limitation by adopting a novel method -
text mining based bibliographic analysis - to map all factors currently
considered to be relevant to adolescent emotion regulation.
Traditional narrative literature reviews have been shown to be marred by reliance on (small) convenience samples of the literature, confirmation bias,
and an undue emphasis on positive results [@littellEvidencebasedBiasedQuality2008]. 
Text mining, by contrast, is uniquely suited to provide a comprehensive overview of the literature.
It can cover vastly greater corpora than a human reader,
and the process by which text mining gleans insights from the literature is more objective, transparant, and reproducible.
Where human readers might be inclined to structure their reading of the literature around established ideas,
the inherent "fairness" of text mining gives emerging themes in the literature a chance to come to the fore.
Text mining identifies important topics in a body of literature and reveals which constructs are often studied together.
This potentially reveals topics and connections missed by narrative reviewers,
thereby laying the groundwork for future empirical and theoretical work. <!-- CJ To fill out gaps, following up on promising constructs and unify heretofore disparate regions of the lit -->
<!-- SH: this implies that the main contribution of the paper is predominantly methodological is that the case? Is there some primary thesis/argument that will be advanced? It is really important to take a top-down approach to that messaging, beginning here in the first paragraph-->
<!-- Ergens anders: Similarly, although
there are several *relevant* theories, there is no specific theoretical
framework to guide research on adolescents' emotion regulation. Although theory
development is beyond the scope of this paper, we set out to generate a
proto-theoretical nomological network of the potential risk factors,
manifestations, and outcomes of emotion regulation in adolescence. We discuss
how this nomological network relates to existing relevant theory, and conclude
with recommendations for future theory-generating efforts.-->

@@

The results of our text mining analysis of the empirical literature on adolescents' emotion regulation will be best understood against the backdrop of the existing theoretical landscape.
We distinguish the topics covered in this theoretical review visually to highlight new issues
in the subsequent text mining analysis.
This allows us to see in what respects the text mining analysis reflects existing theory,
and in what respects it complements it.
We provide only a summary theoretical review here, as other recent publications offer more detailed reviews of theories of emotional development [@bussTheoriesEmotionalDevelopment2019] and emotion regulation in adolescence [@riedigerEmotionRegulationAdolescence2014].
These prior reviews remark that,
although many theories are *relevant* for emotion regulation development in adolescence,
few have addressed this topic directly.
Fewer theories still have comprehensively addressed important predictors of development in this life stage,
and none directly guide contemporary research in the field [see @bussTheoriesEmotionalDevelopment2019].
There is thus a need for more integrative theory formation [see @riedigerEmotionRegulationAdolescence2014].
Inductive analysis of the empirical literature may constitute a first step to this end.

Among the oldest relevant theories of adolescents' emotional development is Hall's notion of "storm and stress" [see
@arnettAdolescentStormStress1999]. It describes how hormonal changes diminish
self-control and increase reactivity, leading to difficulties in emotion
regulation, conflict with parents, and risky behavior.
In modern theories, this notion of diminished self-control and increased emotional reactivity has been retained - although it is now considered to be a normative change that facilitates emotional maturation
[@croneUnderstandingAdolescencePeriod2012], at the risk of emotional
disturbance [@arnettAdolescentStormStress1999; @leeAdolescentMentalHealth2014].

@@

@@

This emphasis on social influences and neurocognitive development is reflected in many theories.
Some of these focus primarily on neurocognitive development.
For example, polyvagal theory closely links emotional experience
- and regulation - to autonomous nervous system functioning
[@porgesOrientingDefensiveWorld1995].
A more recent neurocognitive theory relevant to adolescents' emotion regulation development is Crone
and Dahl's model of social-affective engagement and goal flexibility
[@croneUnderstandingAdolescencePeriod2012]. Like other authors 
[e.g., @caseyBrakingAcceleratingAdolescent2011; @craccoEmotionRegulationChildhood2017],
Crone and Dahl argue that the developmental
asymmetry between motivational and inhibitory brain circuits gives rise to a
"maturity gap" in middle adolescence. 
What distinguishes Crone and Dahl from related writings
is the greater attention to adolescents' diverging destinies:
the question why some youngsters flourish while others languish.
They argue that adolescents' cognitive engagement is dynamically responsive to
social and motivational goal salience. This flexibility, on the one hand,
prepares adolescents to effectively engage cognitive systems in novel
challenging situations in a way that facilitates developing mature regulatory
abilities. On the other hand, it places them at risk to act impulsively in
pursuit of peer approval. In terms of explanans,
this theory focuses primarily on cognitive factors
and the role of peers, with less attention to factors such as parenting.
Although this theory focuses on adolescence specifically,
an important limitation is that it only tangentially relates to emotion regulation.

Other theories emphasize socialization to a greater extent.
One such theory is Morris' tripartite model, which focuses specifically on parents' role in emotion regulation development [-@morrisRoleFamilyContext2007].
It describes three pathways through which parents shape emotion regulation
development: Through observation and modeling, parenting practices, and the
emotional family climate, which in turn involves attachment and marital
relationship quality. Morris and colleagues also emphasize the relevance of
fathers and siblings, and others have adapted the tripartite model to describe
the role of peers in adolescents' emotion regulation development
[@reindlSocializationEmotionRegulation2016].
A more abstract take on socialization is found in @holodynskiDevelopmentEmotionsEmotion2006's
internalization model of emotional development. 
Unique aspects emphasized in this theory are the interplay between emotion and communication,
and the internalization of the cultural symbolic function of emotion.
These theories explain socialization in great detail,
but one potential limitation is that tey are not embedded in a larger unifying framework.
<!--Like Sroufe, Holodynski describes an age graded transition from
interpersonal to intrapersonal emotion regulation.
In doing so, Holodynski applies Vygotsky's theory of development to the domain of
emotion, and presents a detailed integrated model of emotional experience and
regulation.-->

Looking beyond the developmental literature,
theories of the phenomenon of emotion regulation offer additional insight into
intra-individual drivers of emotion regulation development.
Perhaps the most influential theory is Gross'
[-@grossHandbookEmotionRegulation2013] process model, which describes the
process of emotion regulation from eliciting cue to ultimate response.
According to Gross, individuals use strategies to modulate the different stages of this process,
consciously or otherwise. Culture plays a role too, as the effectiveness, desireability, and consequences of different strategies depend on the social context [see
@bariolaChildAdolescentEmotion2011]. Similar to Gross' theory, the social
information processing theory of emotion also describe the role of cognitive
processes and strategies in emotion experience and regulation
[@lemeriseIntegratedModelEmotion2000].

Finally, given our interest in risk factors that render adolescents susceptible
to emotional difficulties, we should mention two theories widely invoked to frame research on developmental influences: Bronfenbrenner's bioecological model, and Sameroff's
transactional model. Bronfenbrenner's model
[@bronfenbrennerBioecologicalModelHuman2007] describes how the environment
shapes individual development. Each individual is imbued with certain
biological predispositions, and develops over time, in interaction with
contextual influences. These influences range from the microsystem, composed of
those people close to the individual, to the macrosystem, consisting of
indirect political and economic influences, to the exosystem, consisting of
cultural norms and values. Sameroff's model is somewhat compatible with the
bioecological model [@sameroffUnifiedTheoryDevelopment2010], but focuses more
on the interplay between nature and nurture. It conceptualizes development as a
product of reciprocal influences between the child and the environment.
Sameroff distinguishes between proximal influences, for instance, through
parents (the microsystem in Bronfenbrenner's model), and distal influences;
structural factors indirectly shaping development, like socio-economic status,
schools, and the community (macro- and exosystem). With increasing age, distal
influences gradually gain ground on proximal influences.
These theories are broad enough to contextualize any developmental study,
but limited by a lack of specificity, which hampers their utility in generating hypotheses.
<!-- RK: What do you take from these broad perspectives for your RQ?-->
<!--SH I am not sure what contribution this paragraph ultimately makes - you should consider condensing it substantially to just note that these theories have something to say about emotional development but are not adolescent-specific-->
<!--Theories like this are particularly relevant to a fine-grained
understanding of the process of emotion regulation, but their developmental
relevance has unfortunately not yet been considered (REF Buss). -->
<!--Parents are widely considered to be the primary proximal influence driving
emotion regulation development.
Yet several limitations remain.
@coe-odessEmergentEmotionsAdolescence2019;
instead takes an inductive approach to map the correlates of adolescents'
emotion regulation based on all available literature.

@@

### Shortcomings of existing theory

<!--Consider splitting this up and putting the shortcomings next to the existing theories-->
Despite the abundance of relevant theory,
the existing literature has several limitations when the goals is to
identify which
risk factors render some adolescents more susceptible
to maladaptive emotional development than others.
One crucial shortcoming is that most theories lack of explicit attention to the life stage of adolescence.
It is questionable whether theories focused on different ages can be generalized to adolescents,
because this stage differs qualitatively from infancy, childhood, and adulthood [@bariolaChildAdolescentEmotion2011].
A related limitation is that many relevant theories lack
an explicit developmental component <!--, and thus lack a well-substantiated
understanding of developmental processes--> [see
@bussTheoriesEmotionalDevelopment2019;
@croneUnderstandingAdolescencePeriod2012]. 
Perhaps most importantly, however, these theories
vary widely in scope: Some are broad but somewhat non-specific, such as the biopsychosocial models of Bronfenbrenner and Sameroff, and others describe a specific phenomenon, but lack a broader perspective.
It would be beneficial to bridge these levels of analysis.
Based on these shortcomings,
there appears to be a need for more theory generation,
in order to provide a unified framework that could guide future empirical work.
<!--Such a theory should focus on -->
The present study lays the groundwork for such theory development,
by providing an inductive conceptual
review of the field.
Concepts covered in the preceding theoretical review will be tagged in the text mining analysis,
to highlight the contribution of the inductive approach.

@@

Whereas theory provides a top-down understanding of an area of research,
literature reviews can provide a bottom-up, inductive understanding. Given the
noted absence of a single overarching theory, reviews might provide additional
insight into factors considered relevant in the etiology of adolescents'
emotion regulation competencies. For example, a review by
@bariolaChildAdolescentEmotion2011 addresses individual psychological factors
such as temperament, and biological factors like neurocognitive development and
genetic predispositions. Furthermore, the authors address proximal social influences,
including parents, teachers, and peers, and specific mechanisms through which
these individuals exert their influence, including parenting and modeling.
Finally, they address distal factors, including the role of culture and the
media. Barriola and colleagues also 
<!--most notably, they call for a robust theoretical framework to guide future
research.--> call for future research to address parents' role beyond early
childhood.
They further argued that the role of fathers in emotion socialization warrants further scrutiny - a topic that is now receiving more attention [@vanlissaRoleFathersMothers2019;
@vanlissaMothersFathersQuantitative2020].

Another review by @coe-odessEmergentEmotionsAdolescence2019 offers a nuanced
discussion of several issues that complement prior publications in this field.
For instance, the authors cover the implications of physiological changes in
detail, including neurocognitive development and pubertal maturation. As
adolescents become increasingly individuated, conflict with parents peaks. This
conflict, in turn, impacts emotion regulation, both in terms of day-to-day mood
variability and dispositional emotion dysregulation [see also
@vanlissaCostEmpathyParentadolescent2017].
Compared to children, adolescents also become increasingly oriented towards peers.
This includes increased
sensitivity to social status and norms, along with the associated increase in
peer pressure and risk taking. Pubertal development also initiates the
emergence of sexual and romantic behavior, and the intensification of both
biological sex differences and gender stereotyped behavior. With regard to the
process of emotion regulation, Coe-Odess and colleagues discuss the importance
of strategies, and point out that, in addition to negative emotionality,
positive emotionality also peaks in adolescence. Relatedly, the authors
describe how hormonal changes precipitate an increased stress response, which
might help explain adolescents' greater susceptibility to emotion
dysregulation. Finally, going beyond the implications of cognitive development
discussed in other publications, the authors discuss how an greater capacity
for abstract thought relates to identity formation - a key challenge in
adolescence [@meeusStudyAdolescentIdentity2011] - and to increased emotional
understanding, and by extension, empathy [see also
@vanlissaLongitudinalInterplayAffective2014].

There are notable parallels between the relevant factors highlighted by these
narrative reviews, and the aforementioned theoretical literature.
Nevertheless,
these literature reviews also touch upon issues that have received little
attention in theoretical work.
These include individual differences, both at the biological and psychological level, including genetic predisposition, hormones, pubertal onset, gender, sexuality, temperament, identity, empathy, and stress.
Proximal influences not covered in theory include the role of media, norms, and social status.
Thus, reviews of the empirical literature can contribute additional insight into key factors in adolescents' emotion regulation development.
One remaining limitation is that all reviews in this field have been unstructured narrative reviews.
The present publication seeks
to complement preceding work by conducting a comprehensive empirical
literature review, and mapping the factors associated with adolescent emotion
regulation using text mining.

@@

<!-- SH: ultimately I think that the introduction is too long - considering that the introduction, itself, is a literature review to some extent, I don't come away with a clear delineation between the literature review up this point and the new work you are going to contribute. I think you need to review the Introduction with an eye on focusing the discussion on the problems/gaps that exist and how the lit review method usually used are insufficient for addressing those issues-->

@@

The present paper aims to develop a nomological network of the constructs
related to adolescent emotion dysregulation, based on a systematic review of
the literature. A nomological network is a diagrammatic representation of a
phenomenon; a proto-theoretical device that describes relationships between
constructs relevant to the theory [see @alaviAligningTheoryMethodology2018]. It is a precursor to a more
explicit theory of the phenomenon. The present paper uses an inductive approach
to develop this nomological network. <!-- CJ Consider removing the following if the purpose is sufficiently clarified in the introduction -->
First, we conducted a systematic search to
elicit a corpus of relevant literature. Second, we used text mining techniques
to extract relevant constructs from the corpus. Third, we used a dictionary to
pare down the extracted constructs to meaningful superordinate categories.
Fourth, we mapped interrelations between these constructs. Fifth, we classified
contstructs as potential predictors or outcomes.
<!--, and we categorize predictors
by level of analysis-->
<!-- (CJ: Sameroff, which level of biopsychosocial)-->.
<!-- t, using text mining to map potential predictors of adolescent emotion
dysregulation.
identify relevant constructs of adolescents’ emotion regulation development,
and moderators of parents’ role therein. The resulting insights are
consolidated into theory.
The present study intends to map the extant literature
First, I will systematically review predictors currently considered relevant in
the adolescent emotion regulation literature.  -->

@@

All searches were conducted on Web of Science. The search strategy was based on
procedures described by Staaks [@staaksSystematicReviewSearch]. First, we
manually constructed a reference set of 15 articles. Then we constructed a
search string to retrieve these articles from Web of Science. The search was
overly inclusive, returning 29 records. As these were all highly relevant, we
updated the reference set to include all 29 results. Next, we tested our search
string, which consisted of synonyms of emotion regulation and adolescence: <!--
### Reference set Our reference set is documented in `reference_set.bib`. -->
```
TS=("emotio* regulation" OR "anger regulation" OR "sadness regulation" OR
"emotion* competence" OR "emotion* adjustment" OR "emotio* dysregulation" OR
"anger dysregulation" OR "sadness dysregulation" OR "emotio* problem*" OR
"emotion* maladjustment") AND TS=(adolescent* OR teen* OR pubert* OR youth)
```
This string returned 6653 results, and matched 25 of the 29 records in the
reference set. Three search terms could be added to match all 29 reference set
items. The terms `"emotio* socialization" OR "emotio* processes"`, as synonyms
of emotion regulation, added 191 new hits. However, most of these did not meet the inclusion criteria used for screening, as explained below.
The term `"development*"`, as synonym
of adolescence, added 3628 new hits, many of which were not focused on the age
range of adolescence. We thus deemed these terms to be overly inclusive, and
proceeded with the original search string above.
```{r readrecs}
filenam <- "recs_6653.RData"
if(!file.exists(filenam)){
  f <- list.files("./recs/18-3-2020/", full.names = TRUE)
  f <- readFiles(f)
  recs <- convert2df(f)
  saveRDS(recs, filenam)
} else {
  recs <- readRDS(filenam)
}
```

@@

<!-- it might be useful to insert a sentence or two when you are using a method many readers are not familiar with, just to explain the utility of the chose method (what it does/doesn't do potentially as compared to other options)-->
To assess the homogeneity of the corpus, we conducted topic modeling using latent dirichlet allocation [@bleiLatentDirichletAllocation2003].
For this analysis, we used the term frequency/inverse document frequency (TF-IDF) to select terms
used frequently in a document, but not used frequently in the corpus,
which could therefore be more diagnostic of subgroup membership.
Selection terms with an TF-IDF greater than the median resulted in a corpus of `r lda_dims[1]` documents and `r lda_dims[2]` terms.
We considered a range from 2-20 topics, evaluating fit based on the BIC, and interpretability based on the entropy of the posterior document/topic probabilities.
The BICs followed a near-perfect linearly increasing trend, indicating that no subcorpora could be identified.
Congruently, all entropies were near-zero, which means that the posterior document/topic probabilities were effectively uniformly distributed.
Thus, no interpretable subcorpora could be identified,
and we proceed with an analysis of the whole sample. <!-- Probably because each set of keywords has only a few indicators. -->

@@

# General Discussion
